Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-10-17 slides/ERE_lunch.Rmd
Updated manuscript intro and methods

mpas <- sf::read_sf(here::here("raw_data", "spatial", "WDPA_Mar2018"),
        layer = "WDPA_Mar2018_marine-shapefile-polygons",
        quiet = T,
        stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(gis_m_area > 250000)

@@

effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines") %>% 
  arrange(!treated) %>% 
  ggplot(aes(x = date, y = hours, color = treated)) +
  geom_smooth(method = lm, formula = y ~ splines::bs(x, 4), aes(group = paste(treated, post))) +
  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.5) +
  ggtheme_plot() +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
```

>>>>

mpas <- sf::read_sf(here::here("raw_data", "spatial", "WDPA_Mar2018"),
        layer = "WDPA_Mar2018_marine-shapefile-polygons",
        quiet = T,
        stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(gis_m_area > 250000,
         no_tk_area > 0)

@@

effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines") %>% 
  arrange(!treated) %>% 
  ggplot(aes(x = date, y = hours, color = treated)) +
  geom_point(size = 1, position = position_jitter(width = 1, height = 0), alpha = 0.1) +
  geom_smooth(method = lm, formula = y ~ splines::bs(x, 4), aes(group = paste(treated, post))) +
  ggtheme_plot() +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
```
